### 2015-12-02 clusters.tex
ack, abstract, summary, smaller changes

\begin{center}
\begin{tabular}{lcr}
 Ne(2s$^{-1}$) Ne &$\rightarrow$ & Ne(2p$^{-1}$) Ne(2p$^{-1}$)\\
 Ne(2s$^{-1}$) Ar &$\rightarrow$ & Ne(2p$^{-1}$) Ar(3p$^{-1}$)
\end{tabular}
\end{center}

@@

The peak structure of one main peak and a shoulder at higher energies has been
discussed for the NeAr before. Theoretical investigations indicate that the
shape might be caused by several vibrational levels of the NeAr dimer
being involved in the decay process ($v=0,1,2$) \cite{Scheit06}. However, very
recent experimental results of the ICD in the NeAr dimer show a symmetric peak
without a shoulder \cite{OKeeffe14}. In order to explain this, the authors assume
a bond contraction of the Ne$^+$Ar to happen prior to the decay.
This nuclear rearrangement would contradict the
theoretically predicted lifetime of the system and therefore they propose
the prior value to be wrong and give an estimate for a higher lifetime.
Since the shoulder appears in the spectrum of clusters only and not in the
dimer spectra, we interpret these experimental results of the dimer to confirm our
findings, that the shoulder stems from ICD with interaction partners of the
next shell \cite{Fasshauer14_1}. This hypothesis is furtherly supported by the
fact that no bound vibrational levels exist in small neon clusters and the
shape of the peak is observed for the NeNe-ICD as well \cite{}.
Because of the lack of eventually involved vibrational levels, we will
focus on the NeNe-ICD part of the ICD electron spectra of the NeAr clusters
and analyze them in more detail.

%Using the simulations of
%cluster model structures, we were able to explain the shoulders of both
%the NeNe-ICD and the NeAr-ICD peak by decay with decay partners of the next
%shell.

%While the shoulder of the NeAr-ICD peak might be able to be explained
%by a decay of higher vibrational levels \cite{Scheit06} bound vibrational
%states do not exist in pure neon clusters. \cite{} 
%Other decay processes resulting in secondary electrons of the corresponding
%kinetic energies between \unit[2.5]{eV} and \unit[3.5]{eV} are not known.
%Therefore, we can conclude that this shoulder stems from next shell ICD.
%In the following, we will zoom in to the NeNe-ICD part of the spectra
%of Figure xyz of Ref. \cite{Fasshauer14_1} and analyze them in more detail.

@@

>>>>

\begin{center}
\begin{tabular}{lcr}
 Ne(2s$^{-1}$) + Ne &$\rightarrow$ & Ne(2p$^{-1}$) + Ne(2p$^{-1}$) + $e^-_{ICD}$\\
 Ne(2s$^{-1}$) + Ar &$\rightarrow$ & Ne(2p$^{-1}$) + Ar(3p$^{-1}$) + $e^-_{ICD}$
\end{tabular}
\end{center}

@@

The peak structure of one main peak and a shoulder at higher energies has been
discussed for the NeAr before. Theoretical investigations indicate that the
shape might be caused by several vibrational levels of the NeAr dimer
being involved in the decay process ($v=0,1,2$) \cite{Scheit06}. However, very
recent experimental results of the ICD in the NeAr dimer show a symmetric peak
without a shoulder \cite{OKeeffe14}. In order to explain this, the authors assume
a bond contraction of the Ne$^+$Ar to happen prior to the decay.
This nuclear rearrangement would contradict the
theoretically predicted lifetime of the system and therefore they propose
the prior value to be wrong and give an estimate for a higher lifetime.
Since the shoulder appears in the spectrum of clusters only and not in the
dimer spectra, we interpret these experimental results of the dimer to confirm our
findings, that the shoulder stems from ICD with interaction partners of the
next shell \cite{Fasshauer14_1}. This hypothesis is furtherly supported by the
fact that
in the clusters the decay rate scales approximately linearly
with the number of nearest ineighbour decay partners.
In other words, the lifetime of the
singly ionized initial state is only a fraction of the dimer's lifetime and
therefore, the nuclear motion will be even less important than in the dimer.

In the neon dimer several vibrational states of the ionized initial state are
involved in the decay. \cite{Santra00_1} However, in clusters the nuclear
motion might not be fast enough to play a role due to the manifold of
decay partners and the resulting shortening of the lifetime.
In the following, we will focus on the NeNe-ICD part of the
ICD electron spectra of the NeAr clusters and analyze them in more detail.

@@

Two experimental ICD electron spectra of clusters
with a mean cluster size $<N>$ between 47 and 512 atoms
are available in the literature.
\cite{Marburger03,Barth06_2} 
The first experimental spectrum shows a very
broad ICD electron peak without an unambiguously assignable peak structure,
whereas the later results shows a main peak of ICD electrons and a smaller peak
at slightly higher kinetic energies (at around \unit[3]{eV})
that was not even assigned to be an ICD peak in the original work. This peak
corresponds to the decay with non-nearest neighbours. However, a further peak
structure is not visible.
